Quantum Hoare Type Theory

### 2020-10-26 ms-paper/ms-paper.tex
Refine teleport example in appendix C

\usepackage{listings}
\lstloadlanguages{Haskell}
\lstdefinelanguage{QHaskell}{
	language     = Haskell,
	morekeywords = {Qbit, U, C, Pure},
}

@@

\section{Teleportation}
\label{app:teleport}
\todo{TODO: Refine assertions}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi a : Qbit. \Pi e : Qbit
        {(Id(a, -) /\ entangled(e)}
           r : (Bit o* Bit)
        {\top}
      = \a.\e.do apply CNOT to [a, e];
                 apply H to a;
                 return (measure a, measure e)
\end{lstlisting}

\subsection{Bob's circuit}
\begin{lstlisting}[language=QHaskell]
bob : \Pi m1 m2 : Bit. \Pi e : Qbit
      {entangled(e)}
         r : Qbit
      {(Id(r, -)}
      = \m1.\m2.\e.do if m1 then (apply Z to e) else ();
                      if m2 then (apply X to e) else ();
                      return e
\end{lstlisting}

\subsection{Teleport}
\begin{lstlisting}[language=QHaskell]
teleport : \Pi q : Qbit. x : Pure.
           {Id(q, x)}
              r : Qbit
           {Id(r, x)}
         = \q.do (a, b) <- bell;
                 (m1, m2) <- alice q a;
                 tq <- bob m1 m2 b;
                 return tq
\end{lstlisting}

>>>>

\usepackage{listings}
\lstloadlanguages{Haskell}
\lstdefinelanguage{QHaskell}{
	language     = Haskell,
	morekeywords = {Qbit, U, C, Bit},
}

@@

\section{Teleportation}
\label{app:teleport}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi q : Qbit. \Pi a : Qbit
        {q =q (alpha |0\> + beta |1\>) /\ (a, e) =q |\Phi+\>}    -- ie, a is entangled with ghost var e
           (m1, m2) : (Bit o* Bit)
        {  (m1, m2) = 00 /\ e =q (alpha |0\> + beta |1\>)
         \/ (m1, m2) = 01 /\ e =q (alpha |1\> + beta |0\>)
         \/ (m1, m2) = 10 /\ e =q (alpha |0\> - beta |1\>)
         \/ (m1, m2) = 11 /\ e =q (alpha |1\> - beta |0\>)}
      = \q.\a.do (q, a) <= apply CNOT to [q, a];
                 q <= apply H to q;
                 rq <= measure q;
                 ra <= measure a;
                 return (rq, ra)
\end{lstlisting}

\subsection{Bob's circuit}
\todo{TODO provide correct assertions using ghost e}
\begin{lstlisting}[language=QHaskell]
bob : \Pi m1 m2 : Bit. \Pi b : Qbit
      {(b, e) =q |\Phi+\>}
         r : Qbit
      {\top}
      = \m1.\m2.\b.do (m1, b) <= apply C_Z to [m1, b];
                      (m2, b) <= apply C_X to [m2, b];
                      return b
\end{lstlisting}

\subsection{Teleport}
\begin{lstlisting}[language=QHaskell]
teleport : \Pi q : Qbit.
           {q =q (alpha |0\> + beta |1\>)}
              b : Qbit
           {r =q (alpha |0\> + beta |1\>)}
         = \q.do (a, b) <- bell00;
                 (m1, m2) <- alice q a;
                 b <- bob m1 m2 b;
                 return b
\end{lstlisting}
